On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence

### 2017-09-10 Thesis/Draft.tex
Add References

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Draft}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

\section{Abbreviations}\label{abbreviations}

Kullback-Leibler divergence between distributions \(\nu_i\) and
\(\nu_j\): \(\KL(\nu_i||\nu_j)\).

Binary relative entropy:
\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
\(d(0,0) = d(1,1) = 0\).

Kullback-Leibler divergence for two Bernoulli distributions
parameterized by their means \(\mu_i\) and \(\mu_j\):
\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).

Define exponential family of distributions

Define KL Divergence for this family

@@

In this thesis, we consider the thresholding bandit problem. Instead of
identifying the best \(m\) out of \(K\) arms, we aim to find all
distributions out of \(K\) that have a mean at least as large as a
threshold fixed upfront. In the form described in Locatelli et al.
(2016), algorithms in the thresholding bandit problem are evaluated
against a binary loss function penalizing whenever an arm has not been
classified correctly as being above or below the threshold, and thus
focus on exploration similar to algorithms employed for best arm
identification. Indeed, Locatelli et al. (2016) show how their
thresholding algorithm can be used for best arm identification when the
mean of the best arm is known upfront.

@@

To introduce the thresholding bandit problem, consider a game in which
the learner is tasked to find the slot machines within a row of \(K\)
slot machines in a casino that give a mean payoff larger than a fixed
threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
all slot machines at the same time. Instead, he acquires samples
sequentially from one slot machine at a time to learn about their payoff
structure. The learner has a budget of \(T>K\) slot machine pulls. After
\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
from the payoff distribution \(\nu_i\) underlying the slot machine
\(i\). At time \(t\), the learner considers the payoffs he observed so
far in order to choose the next slot machine he would like to pull. Her
decision is lead by the goal to classify the slot machines with
distribution \(\nu_i\) and mean payoff
\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
above or below the threshold with error probability as small as
possible.

The thresholding bandit problem can thus be framed in the literature on
sequential sampling strategies. Even though its name is reminiscient of
the multi-armed bandit setting, the thresholding bandit problem is more
akin to best arm identification and top-\(m\) identification problems
due to its focus on exploration: While the classical multi-armed bandit
problems are concerned with cumulative regret which increases
\emph{during} sampling, best arm identification and thresholding bandits
collect loss only once \emph{after} the sampling procedure (compare
Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
Kalyanakrishnan, 2013). As we will see in
\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
are very related.

\subsection{\texorpdfstring{Setup
\label{sec:Setup}}{Setup }}\label{setup}

Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
idea of multi-armed bandits, we call the distributions arms, and
observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
learner is interested in learning about the structure of the arms; in
particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
different arms. However, at time \(t\) the learner cannot observe a
reward from every distribution but must select a single arm \(I_t\) from
which she would like to observe the reward \(X_{I_t,t}\). Often,
adaptive sampling strategies makes the decision of which arm to pull by
computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
of indexes can be called strategy (Kaufmann et al., 2012) which makes it
clear that the strategy is adapted as more observations are collected.
Strategies of this kind are also called index policies.

@@

\subsubsection{\texorpdfstring{Proof of Theorem
\ref{theorem:LocatelliTheorem4}}{Proof of Theorem }}\label{proof-of-theorem}

@@

Given that we do not follow a uniform sampling strategy, we know that at
time \(T\), some arms will have been pulled more frequently than others.
In particular, some arms will have been pulled more than \(T/K\) times.
How often an arm is pulled can be related to the individual arm's
contribution to the overall complexity measure. Let \(h_i\) be a measure
of arm \(i\)'s individual problem complexity and write for the overall
problem complexity \(H = \sum_{i = 1}^{K} h_i\). Then arm \(i\)
contributes a share of \(h_i/H\) to the overall problem complexity. We
can now show that there exists an arm that has been pulled at least as
often as the share of his complexity contribution.

@@

\subsubsection{Check Separation
Condition}\label{check-separation-condition}

@@

If we write the lower bound as
\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
and the upper bound as
\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
we see that \(LB\) and \(UB\) match up to multiplicative constants and
the \((\log(T)+1)K\) term which is negligiable in comparison with the
exponent for large \(T\) as shown in Locatelli et al. (2016), which
makes the APT algorithm order optimal.

@@

\begin{itemize}
\tightlist
\item
  Mention Optimality (Upper Bound matches lower bound)
\item
  Anytime
\end{itemize}

One of the APT algorithm's main features is its simplicity. The sampling
rule is very straightforward, and, as highlighted in Locatelli et al.
(2016), it does not require any knowledge about the type of
sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
algorithm immediately applicable in practice while it still enjoys its
upper bound on the expected regret. This is in particular worth
highlighting when comparing APT to algorithms used in the best arm
identification or Top-\(m\) setting. As alluded to in
\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
require knowledge about the corresponding complexity upfront (Audibert
et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
being, that to know the complexity, the experimenter has to know all
means up to a permutation of the arms. This, of course, is not given in
practice. Thus alternative algorithms try to estimate the complexity
online which can be difficult as especially in the beginning plug-in
estimates based on the estimated means may lead to wrong estimates of
the complexity, which in turn leads to poor budget allocation based on
mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
hand, the sequential sampling strategy has to rely on some estimate.
While the APT algorithm does not explicitly estimate the complexity, the
gaps that serve as index are essentially the same. Faced not with
sub-Gaussian but more heavy-tailed distributions, these estimates might
well lead to poor performance.

Here, the APT algorithm shows room for improvement, as also mentioned in
Locatelli et al. (2016). The problem is that the assumptions for the
bounds no longer hold as arms are less sub-Gaussian; of course the
complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
index are motivated by sub-Gaussian distributions. The more one moves
away from those, the less appropriate these quantities become. In
particular, the empirical mean will be less (or not at all) concentrated
around the true mean and more impacted by outliers which are more likely
under non sub-Gaussian distributions. Locatelli et al. (2016) thus
refers to Bubeck et al. (2013a) which considers solutions for
multi-armed bandits that are based on heavy-tail distributions. By using
more robust estimators of the mean, one could equip the APT algorithm to
deal with such distributions.

Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
estimates of the variance of the arms for their algorithms for the
thresholding bandit problem and try to thereby improve upon the
performance of the APT algorithm. While their simulations show promising
results, their bounds rely on the assumption of bounded reward
distributions. Thus their algorithms are not necessarily able to improve
upon the assumption of sub-Gaussian distributions made by Locatelli et
al. (2016). We will continue to discuss their results in
\autoref{chap:VarianceBasedAlgorithms}.

@@

\[
\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
\]

@@

\[
\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
\]

@@

\[
\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
\]

This is of course equal to the Gaussian KL-divergence described before.
This approximation, however, suffers for heavily for very small values
of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
contrast to the complexity measure \(H\) based on the Gaussian
KL-divergence, a complexity measure based on the Bernoulli KL-divergence
would evaluate two arms as differently difficult if their absolute
distance to the threshold is the same, but they lie on different sides
of the threshold.

Thus similarly to how UCB algorithms in the cumulative regret setting
have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
also the APT algorithm offers room for improvement. As a more explicit
example of such adaptation, consider the case of Top-\(m\)
identification described in Kaufmann et al. (2016). The authors develop
a lower bound based on KL-divergence, and note that ``This
information-theoretic lower bound permits to interpret the quantity
\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
Bernoulli distributions with very small parameter values arise naturally
in many applications, an improvement in this regard would be valuable.

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

@@

The previous chapter introduces the thresholding bandit problem as
described in Locatelli et al. (2016), and with the APT strategy a first
algorithm that is simple, yet order-optimal for large budgets. However,
we end with the conclusion that a distance measure between the
distributions and the threshold based on the Kullback-Leibler divergence
might be more useful than the simple gap
\(\Delta^2_i = (\mu_i - \tau_i)^2\) employed so far. Indeed, citing
Kaufmann et al. (2016), we note that the complexity \(H\) used so far
can be considered a sub-Gaussian approximation of a better complexity
measure based on information theoretic measures like the
Kullback-Leibler divergence.

In order to give more intuition to why that is the case, and in what
ways information theoretic measures can be introduced to measure the
complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
Garivier and Kaufmann (2016). The latter describes a strategy based on
Kullback-Leibler divergences for the best-arm identification problem,
while the first derives complexity measures based on the divergence.
Ideally, their work offers methods that can inform our work of extending
the thresholding bandit problem. In what follows, we adopt the notation
of Kaufmann et al. (2016) to ease a comparison with their arguments.

@@

Instead of the thresholding bandit problem, Kaufmann et al. (2016)
consider the problem of identifying the best \(m\) out of \(K\) arms,
that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
by \(K\) arms characterized by probability distributions \(\nu_a\),
\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
find the \(m\) out of \(K\) arms with the largest expected reward. This
set of arm indexes is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
et al. At the end of the sampling procedure, after \(T\) samples
(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
return a classification \(\hat{\mathcal{S}}_m\). This classification is
then evaluated by the loss function
\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
This binary loss is similar to the loss in the thresholding bandit. We
can now define a strategy of the learner as
\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
how an arm is chosen, how many samples are observed, and how the arms
are eventually classified.

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={On Pure Exploration, Thresholding Bandits, and Kullback-Leibler Divergence},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{On Pure Exploration, Thresholding Bandits, and Kullback-Leibler
Divergence}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

@@

In this thesis, we consider the thresholding bandit problem. While the
name is reminiscient of the cumulative regret multi-armed bandit, the
problem is more similar to the top-\(m\) problem. But instead of
identifying the best \(m\) out of \(K\) arms, one aims to find all
distributions out of \(K\) that have a mean at least as large as a fixed
threshold. Given that an implicit threshold arises in the top-\(m\)
problem between the \(m\)-th best and the \((m+1)\)-th best arm
(Kaufmann et al., 2016), the two problems share many characteristics. We
discuss this in more detail in
\autoref{chap:KullbackLeiblerPureExploration}. In the form described in
Locatelli et al. (2016), algorithms in the thresholding bandit problem
are evaluated against a binary loss function penalizing whenever an arm
has not been classified correctly as being above or below the threshold,
and thus focus on exploration similar to algorithms employed for best
arm identification. Indeed, Locatelli et al. (2016) show how their
thresholding algorithm can be used for best arm identification when the
mean of the best arm is known upfront.

@@

\subsection{An Example}\label{an-example}

To introduce the thresholding bandit problem, consider a common
situation among internet-based companies. These companies often collect
user feedback to offer reviews and ratings on websites or in apps, or
collect it to improve their services. Netflix lets users rate movies
with ``Thumbs up'' and ``Thumbs down'', apps like Clue ask users a
question per day to learn to predict the user's health and mood. An
online shop might give customers a one-question survey after they make a
purchase. Finally, Foursquare and Yelp ask users to rate coffee shops,
bars, and restaurants.

Consider the problem the latter companies face. Whenever a user reports
that she visited a restaurant, the app would like to ask questions about
her experience. To give a simple example, assume users are not willing
to answer more than one question per restaurant visit, and the app would
like to find out two things: Does the restaurant have good service? Is
the restaurant trendy?

If the feedback that users can give is restricted to binary ``Yes'' or
``No'' answers, then we can model the feedback as Bernoulli random
variables

\[
X_{\text{service}} \sim \text{Ber}(\mu_{\text{service}}) \quad \text{and} \quad X_{\text{trendy}} \sim \text{Ber}(\mu_{\text{trendy}}).
\]

The app will then display a ``Good service'' or ``This place is trendy''
description for the restaurant if \(\mu_{\text{service}}\) and
\(\mu_{\text{trendy}}\) are estimated to be above a certain threshold,
for example \(\tau = 0.5\). That is, more than half of the people would
describe the place as having good service, or as trendy.

To make the app as useful as possible to other users, this information
should be shown as quickly as possible. But even though the app has
thousands of users, not that many people visit a specific restaurant,
and even less people report this back to the app. Thus the company only
has a limited budget of \(T\) potential users from which to collect
samples \(X_{\text{service}}\) and \(X_{\text{trendy}}\) from. How can
the company ask these \(T\) questions to be as confident as possible in
its classification, that is, in the information it displays?

A straightforward way of sampling users would be to ask the two
questions in a round-robin fashion: Ask for ``Service'', then for
``Trendy'', then for ``Service'', \ldots{} Given 100 users, 50 users
give feedback on the service level, 50 users report on the trendiness
level. This however is unlikely to be optimal with respect to the
confidence after 100 samples. Given that the company asks the users
sequentially, there is the option to adapt the sampling strategy over
time: If the first ten users report
\(\sum_{s=1}^{10}X_{\text{service},s}=10\), while
\(\sum_{s=1}^{10}X_{\text{trendy},s}=5\), then the company might already
be quite confident that \(\mu_{\text{service}} \geq \tau = 0.5\), while
this is less clear for \(\mu_{\text{trendy}}\). Instead of continuously
sampling both questions, it might be more useful to collect more
feedback on the trendiness level so as to figure out its position
relative to the threshold. After all, the company would like to use the
100 samples to maximize its confidence in both displayed tips.

Finding the optimal sequential sampling strategy to classify
distributions against a threshold with as much confidence as possible
after a limited budget of samples is the problem described above, and
the problem described by the thresholding bandit problem which we
discuss for the remainder of this thesis. In the following section, we
define the general setting of the thresholding bandit problem.

\subsection{\texorpdfstring{General Setting
\label{sec:Setup}}{General Setting }}\label{general-setting}

Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
idea of multi-armed bandits, we call the distributions arms, and
observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
learner is interested in learning about the structure of the arms; in
particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
different arms, where \(X_{i} \sim \nu_i\). However, at time \(t\) the
learner cannot observe a reward from every distribution but must select
a single arm \(I_t\) from which she would like to observe the reward
\(X_{I_t,t}\). Often, adaptive sampling strategies makes the decision of
which arm to pull by computing an index \(B_i(t)\) for each arm. If
\(T_i(t)\) is the number of samples observed until time \(t\) for arm
\(i\), then is \(B_i(t)\) a function of the past rewards
\(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm \(i\), and w.l.o.g.
\(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of indexes can be
called strategy (Kaufmann et al., 2012) which makes it clear that the
strategy is adapted as more observations are collected. Strategies of
this kind are also called index policies.

@@

\subsubsection{\texorpdfstring{Proof of Theorem
\ref{theorem:LocatelliTheorem4}
\label{sec:UpperBoundProof}}{Proof of Theorem  }}\label{proof-of-theorem}

@@

Given that we do not follow a uniform sampling strategy, we know that at
time \(T\), some arms will have been pulled more frequently than others.
In particular, some arms will have been pulled more than \(T/K\) times.
How often an arm is pulled can be related to the individual arm's
contribution to the overall complexity measure. Let \(h_i\) be a measure
of arm \(i\)'s individual problem complexity and write for the overall
problem complexity \(H = \sum_{i = 1}^{K} h_i\). Then arm \(i\)
contributes a share of \(h_i/H\) to the overall problem complexity. We
can now show that there exists an arm that has been pulled at least as
often as the share of its complexity contribution.

@@

\subsubsection{\texorpdfstring{Check Separation Condition
\label{sec:CheckSeparationCondition}}{Check Separation Condition }}\label{check-separation-condition}

@@

If we write the lower bound as
\(LB = 12(\log(T)+1)K)\exp(-3T/H)\exp(-4) = C_{LB}(\log(T)+1)K\exp(-T/H)\)
and the upper bound as
\(UB = (\log(T)+1)K \exp(2) \exp(-\frac{1}{64R^2}\frac{T}{H}) = C_{UB}(\log(T)+1)K\exp(-T/H)\),
we see that \(LB\) and \(UB\) match up to multiplicative constants and
the \((\log(T)+1)K\) term which is negligiable in comparison with the
exponent for large \(T\) as shown in Locatelli et al. (2016). This makes
the APT algorithm order optimal.

@@

One of the APT algorithm's main features is its simplicity. The sampling
rule is straightforward, and, as highlighted in Locatelli et al. (2016),
it does not require any knowledge about the type of sub-Gaussianity
\(R\), or the complexity \(H\) upfront. This makes the algorithm
immediately applicable in practice while it still enjoys its upper bound
on the expected regret. This is in particular worth highlighting when
comparing APT to algorithms used in the best arm identification or
top-\(m\) setting. As alluded to in \autoref{sec:TheAPTAlgorithm}, many
algorithms that fix the sampling budget upfront (i.e., fixed budget
algorithms as UCB-E or KL-LUCB-E) require knowledge about the complexity
upfront (Audibert et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The
problem however being that to know the complexity, the experimenter has
to know all means up to a permutation of the arms. This, of course, is
not given in practice. Thus alternative algorithms try to estimate the
complexity online which can be difficult as especially in the beginning
plug-in estimates based on the estimated means may lead to wrong
estimates of the complexity, which in turn leads to poor budget
allocation based on mistaken beliefs (compare Garivier and Kaufmann,
2016). On the other hand, the sequential sampling strategy has to rely
on some estimate. While the APT algorithm does not explicitly estimate
the complexity, the gaps that serve as index are essentially the same.
Empirically, we see in \autoref{chap:Experiments} that the problem
described by Garivier and Kaufmann (2016) does also occur for the APT
strategy. Faced not with sub-Gaussian but with more heavy-tailed
distributions, this sensitivity is likely to increase.

Furthermore, as mentioned in Locatelli et al. (2016), the assumptions
for the bounds no longer hold as arms become less sub-Gaussian; the
complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
index are both motivated by sub-Gaussian distributions. The more a
problem deviates from those, the less appropriate the quantities become.
In particular, the empirical mean will be less (or not at all)
concentrated around the true mean and more impacted by outliers which
are more likely under non sub-Gaussian distributions. Locatelli et al.
(2016) thus refers to Bubeck et al. (2013a) which consider solutions for
multi-armed bandits that are based on heavy-tail distributions. By using
more robust estimators of the mean, one could equip the APT algorithm to
deal with such distributions.

Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
estimates of the variance of the arms for their algorithms for the
thresholding bandit problem and try to thereby improve upon the
performance of the APT algorithm. While their simulations show promising
results, their bounds rely on the assumption of bounded reward
distributions. Thus their algorithms are not necessarily able to improve
upon the assumption of sub-Gaussian distributions made by Locatelli et
al. (2016). We will continue to discuss their results in
\autoref{sec:VarianceBasedAlgorithms}.

@@

\[
\KL_{\mathcal{N}}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
\]

@@

\[
\KL_{\text{Ber}}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
\]

@@

\[
\KL_{\text{Ber}}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
\]

This is equal to the Gaussian KL-divergence described before. The
approximation, however, suffers heavily for very small values of
\(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
becomes asymmetric in its first argument when \(\tau \neq 0.5\). Thus,
in contrast to the complexity measure \(H\) based on the Gaussian
KL-divergence, a complexity measure based on the Bernoulli KL-divergence
would evaluate two arms as differently difficult if their absolute
distance to the threshold is the same, but they lie on different sides
of the threshold.

Thus similarly to how UCB algorithms in the cumulative regret setting
have been extended to KL-UCB algorithms (Cappé et al., 2013), the APT
algorithm offers room for improvement, too. As a more explicit example
of such adaptation, consider the case of top-\(m\) identification
described in Kaufmann et al. (2016). The authors develop a lower bound
based on KL-divergence, and note that ``This information-theoretic lower
bound permits to interpret the quantity \(H(\nu)\) {[}\ldots{}{]} as a
subgaussian approximation''. Given that Bernoulli distributions with
very small or very large parameter values arise naturally in many
applications, an improvement in this regard would be valuable.

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

@@

The previous chapter introduces the thresholding bandit problem as
described in Locatelli et al. (2016), and the APT strategy as a first
algorithm that is simple, yet order-optimal for large budgets. However,
we end with the conclusion that a KL-divergence based measure of the
distance between the distributions and the threshold might be more
useful than the simple gap \(\Delta^2_i = (\mu_i - \tau_i)^2\) employed
so far. Indeed, citing Kaufmann et al. (2016), we note that the
complexity \(H\) -- and thus the gaps -- used so far can be considered a
sub-Gaussian approximation of a better complexity measure based on
information theoretic measures like the Kullback-Leibler divergence.

In order to give more intuition to why that is the case, and in which
ways information theoretic measures can be introduced to measure the
complexity of bandit problems, we now turn to Kaufmann et al. (2016) and
Garivier and Kaufmann (2016). The latter describes a strategy based on
Kullback-Leibler divergences for the best-arm identification problem,
while the first derives complexity measures based on the divergence.
Their work offers methods that can inform our goal of extending the
thresholding bandit problem. In what follows, we adopt the notation of
Kaufmann et al. (2016) to ease a comparison with their arguments.

@@

Instead of the thresholding bandit problem, Kaufmann et al. (2016)
consider the problem of identifying the best \(m\) out of \(K\) arms,
that is, the top-\(m\) problem. They describe their bandit model
\(\nu = (\nu_1,...,\nu_K)\) by \(K\) arms characterized by probability
distributions \(\nu_i\), \(i \in \mathbb{A} = \{1,...,K\}\), with mean
\(\mu_i\). A learner picks at any time step \(t=1,2,...,\) an arm
\(I_t \in \{1,...,K\}\) for which she observes the independent reward
\(X_{t} \sim \nu_{I_t}\). The learner aims to find the \(m\) out of
\(K\) arms with the largest expected reward. This set of arm indexes is
denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the means
\((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order as the K-tuple
\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
is unique. The class of bandit problems \(\nu\) for which the latter
condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
end of the sampling procedure, after \(T\) samples, the learner is
required to return a classification \(\hat{\mathcal{S}}_m\). This
classification is then evaluated by the loss function
\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
This binary loss is similar to the loss in the thresholding bandit. We
can now define a strategy of the learner as
\(\mathcal{S} = ((I_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
how an arm is chosen, how many samples are observed, and how the arms
are eventually classified.

When introducing the thresholding bandit setting, we did not mention the
fact that there exists an alternative setting in which the budget \(T\)
is not fixed upfront. This setting is called \emph{fixed confidence},
while the case we considered so far is called \emph{fixed budget}. In
the fixed budget setting, we run algorithms for \(T\) samples and then
compare them based on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{S}(\delta)\)for which it holds for
every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
least with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed confidence
case, in which the budget \(T=T_{\delta}\) is no longer fixed upfront,
but becomes a random variable. Algorithms are then compared by their
expected number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer
those which achieve the confidence level \(1-\delta\) with a smaller
expected budget.
